The universal property of direct integrals in W$^*$-categories

### 2018-10-22 direct_integrals.tex
some corrections, plus Example 4.2

\begin{ex}
$\NRep{\cat{N}}$ has a canonical measurable structure of this kind if we declare a collection of objects $\mathcal{S}$ to be measurable if for every Hilbert space $\H$, the set of all $\pi : \cat{N} \to \B{\H}$ which are in is $\mathcal{S}$ is measurable, in the sense of the smallest $\sigma$-algebra which makes the evaluation maps $\pi \mapsto \langle \xi,\pi(a) \xi\rangle$ for $\xi\in\H$ and $a\in\cat{N}$ measurable. As a degenerate special case, for $\cat{C} = \Hilb$ we obtain the discrete $\sigma$-algebra on the objects.

@@

>>>>

\begin{ex}
\label{nrep_measurable}
$\NRep{\cat{N}}$ has a canonical measurable structure of this kind, which we describe in the following. First, a collection of representations $\mathcal{S}$ on a fixed Hilbert space $\H$ is measurable if it is in the smallest $\sigma$-algebra which makes the evaluation maps $\pi \mapsto \langle \xi,\pi(a) \xi\rangle$ for $\xi\in\H$ and $a\in\cat{N}$ measurable. Furthermore, we equip $\Obj{\Hilb}$ with the countable-cocountable $\sigma$-algebra. On $\Obj{\NRep{\cat{N}}}$, we hence put the $\sigma$-algebra consisting of countable or cocountable unions of measurable subsets of $\{ \pi : \cat{N} \to \B{\H} \}$ for varying $\H$.

As a degenerate special case, for $\cat{C} = \Hilb$ we obtain the discrete $\sigma$-algebra on the objects.

@@

\begin{ex}
In the situation of Example~\ref{nrep_measurable}, a family of representations $x \mapsto (\H_x,\pi_x)$ is measurable if and only if the following holds: there is a countable measurable partition $X = \coprod_{n\in\N} X_n$, such that $x\mapsto \H_x$ is constant on each part $X_n$, and such that on each part $X_n$, the function $x \mapsto \pi_x$ is measurable.

More concretely, let us consider $\Rep{C(S^1)} \cong \NRep{C(S^1)^{**}}$ and $X := S^1$, equipped with its usual $\sigma$-algebra and measure (the normalization is irrelevant). To every $x\in X$ we assign the Hilbert space $\C$, together with the unitary given by multiplication by $x$. This induces a representation of $C(S^1)$, or equivalently a normal representation of $C(S^1)^{**}$, as usual via functional calculus, which in this case simply corresponds to function evaluation at $x\in S^1$. Measurability of the function $x\mapsto \pi_x$ amounts to measurability of each map $x\mapsto \langle\xi,\pi(a)\xi\rangle$ for $\xi\in\C$ and $a\in C(S^1)^{**}$, or equivalently measurability of $x\mapsto |\xi|^2 a(x)$, which is obvious, since the evaluation at $x$ factors through the canonical homomorphism $C(S^1)^{**} \to \mathcal{L}^\infty(S^1)$, where $\mathcal{L}^\infty$ denotes the algebra of bounded measurable functions (without modding out by null sets).
\end{ex}
